Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-04-27 PAPER/main.tex
changed table, changed various sections

\begin{definition}
	\label{defn:scspp}
	Let $\mathcal{S} = S_1, S_2, ..., S_k$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ < W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$. Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
\end{definition}

@@

% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..

Let $\mathcal{M}$ be an instance of the COP of cardinality $n$. We model each of the values of all elements in $\mathcal{M}$ as a vertex on a graph $G$, and assign each vertex a value from $\mathcal{M}$ in non-decreasing order. A pair of vertices, called ``dominating vertices'' are then added to the graph, both of which are assigned values equal to $\tau$. These dominating vertices aid the solution process, and are removed at the end. Thus, the graph $G$ has $2n+2$ vertices.

@@

Now, we add to $G$ a set of ``red'' edges, $R$, that consists of edges between vertices whose values equal or exceed $\tau$, provided they are not partners. This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}.

@@

\begin{figure}	
\centering
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/partners}
	\caption{$G = (V, B)$}	
	\label{fig:partners}
\end{subfigure} \hspace{40pt}
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/threshold}
	\caption{$G=(V, B \cup R)$}	
	\label{fig:threshold}
\end{subfigure}
\caption{Example construction of $G$ using instance $\mathcal{M}$ from the example above.}
\label{fig:partners/threshold}
\end{figure}

The following definition now describes a variant of the classical Hamiltonian cycle on a graph $G$.

@@

Therefore, the aim of this algorithm is to construct an alternating Hamiltonian cycle on $G$. Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, every edge in $B$ must be present in the alternating Hamiltonian cycle. Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$, such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition $\ref{defn:althamcycle}$.

@@

\begin{figure}	
	\centering
	\begin{subfigure}[h]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{$G' = (V, B \cup R')$}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[h]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{$G' =(V, B \cup R')$ planar}	
		\label{fig:mps}
	\end{subfigure}
	\caption{Subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components.}
\end{figure}

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:copsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$. $G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_{\lambda}$. If there is only one component on $G'$, i.e. $\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle. The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $R$ to be used as bridges between the components of $G'$, and will replace certain edges in $R'$.

@@

The sets $R_1, R_2, ..., R_k \subseteq R$ created during this process are then analysed. In the event that BR has been unable to produce a single set $R_1$, the components $C_1,..., C_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists. If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':

@@

\begin{table}[!htb]
\centering
\caption{$n = 100$}
\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
	\noalign{\smallskip}
	& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
	\hline\noalign{\smallskip}
	$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
	\noalign{\smallskip}
	\hline 
	\noalign{\smallskip}
	0.0 & 0.119930 & 0.119930 & 0.119930 & 0.234780 & 0.234780 & 0.234780 & 0.464660 & 0.464660 & 0.464660 \\
	0.1 & 0.190373 & \textbf{0.209209} & 0.195007 & 0.368315 & \textbf{0.403484} & 0.372649 & 0.653776 & \textbf{0.662649} & 0.654527 \\
	0.2 & 0.241823 & \textbf{0.291742} & 0.252201 & 0.455307 & \textbf{0.537355} & 0.464804 & 0.740613 & \textbf{0.743163} & 0.74212 \\
	0.3 & 0.308598 & \textbf{0.423971} & 0.330489 & 0.552257 & \textbf{0.700541} & 0.573676 & 0.817858 & 0.801526 & \textbf{0.820929} \\
	0.4 & 0.387256 & \textbf{0.634770} & 0.435353 & 0.648313 & \textbf{0.860270} & 0.688716 & 0.874070 & 0.835449 & \textbf{0.878158} \\
	0.5 & 0.491093 & \textbf{0.900872} & 0.586398 & 0.747025 & \textbf{0.953757} & 0.806812 & 0.915534 & 0.854677 & \textbf{0.920727} \\
	0.6	& 0.612443 & \textbf{0.982422} & 0.753466 & 0.834971 & \textbf{0.962939} & 0.896095 & 0.939964 & 0.864190 & \textbf{0.945036} \\
	0.7 & 0.773879 & \textbf{0.986985} & 0.909705 & 0.916026 & \textbf{0.965898} & 0.959666 & 0.957970 & 0.873854 & \textbf{0.961036} \\
	0.8	& 0.904347 & \textbf{0.987407} & 0.980250 & 0.966750 & 0.967486 & \textbf{0.984634} & 0.964117 & 0.885786 & \textbf{0.965271} \\
	0.9	& 0.978801 & 0.984535 &	\textbf{0.991745} & 0.987382 & 0.967989 & \textbf{0.990479} & 0.968735 & 0.897915 & \textbf{0.968928} \\
	1.0 & \textbf{0.995493} & 0.988851 & \textbf{0.995493} & \textbf{0.992539} & 0.969239 & \textbf{0.992539} & \textbf{0.967834} & 0.904161 & \textbf{0.967834} \\
	\hline
\end{tabular}
\label{table:n100}
\end{table}

>>>>

\begin{definition}
	\label{defn:scspp}
	Let $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ < W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$. Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
\end{definition}

@@

% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
Let $\mathcal{M}$ be an instance of the COP of cardinality $n$. We model each of the values of all elements in $\mathcal{M}$ as a vertex on a graph $G$, and assign each vertex a value from $\mathcal{M}$ in non-decreasing order. A pair of vertices, called ``dominating vertices'' are then added to the graph, both of which are assigned values equal to $\tau$. These dominating vertices aid the solution process, and are removed at the end. Thus, the graph $G$ has $2n+2$ vertices.

@@

Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose values equal or exceed $\tau$, provided they are not partners. This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}.

@@

\begin{figure}	
\centering
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/partners}
	\caption{$G = (V, B)$}	
	\label{fig:partners}
\end{subfigure} \hspace{40pt}
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/threshold}
	\caption{$G=(V, B \cup R)$}	
	\label{fig:threshold}
\end{subfigure}
\caption{Example construction of $G$ using instance $\mathcal{M}  = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$}
\label{fig:partners/threshold}
\end{figure}

Consider the following definition describing a variant of the classical Hamiltonian cycle on a graph $G$.

@@

An alternating Hamiltonian cycle on $G$ would correpsond to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ shows values that can be placed alongside one another feasibly. Thus, by removing the dominating vertices and any incident edges, the remaining alternating Hamiltonian path illustrates the order in which the elements should be placed to produce a feasible solution $\mathcal{T}$.

Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, i.e. the values cannot be changed, and the values in each element cannot be separated, every edge in $B$ must be present in the alternating Hamiltonian cycle. Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.

@@

\begin{figure}	
	\centering
	\begin{subfigure}[h]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{$G' = (V, B \cup R')$}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[h]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{$G' =(V, B \cup R')$ planar}	
		\label{fig:mps}
	\end{subfigure}
	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components, $q = 2$}
	\label{fig:matching/mps}
\end{figure}

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence no feasible solution can be found for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}). $G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_q$. In the case where $G'$ comprises one component, i.e. $q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. However, if $q > 1$, the components of $G'$ must be combined to form an alternating Hamiltonian cycle. To do this, a Bridge Recognition (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.

\begin{itemize}
	\item smaller vertices lexicographical increasing, $v_1,..., v_{n+1}$
	\item larger vertices lexicographical decreasing, $v_{2n+2},..., v_{n+2}$
	\item any edge that doesn't abide by this order should be removed
	\item caused during MMCM, highest indexed vertex could not be matched with current vertex due to being partners, so current vertex is matched with next highest indexed vertex available.
	\item thus list of edges should be $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$.
\end{itemize}

@@

The sets $R_1, R_2, ..., R_k \subseteq R$ created during this process are then analysed. In the event that BR has been unable to produce a single set $R_1$, the components $C_1,..., C_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists. If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following `
`connecting method'':

@@

\begin{table}[!htb]
	\centering
	\caption{$n = 100$}
	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
		\noalign{\smallskip}
		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
		\hline\noalign{\smallskip}
		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
		\noalign{\smallskip}
		\hline 
		\noalign{\smallskip}
		0.0	& 8.35709 & 8.35709 & 8.35709 & 4.26800 & 4.26800 & 4.26800 & 2.15624 & 2.15624 & 2.15624 \\
		0.1	& 5.27284 & \textbf{4.89963} & 5.14404 & 2.72299 & \textbf{2.48800} & 2.69191 & 1.53147 & \textbf{1.51049} & 1.52968 \\
		0.2	& 4.16155 & \textbf{3.46467} & 3.98645 & 2.21096 & \textbf{1.87449} & 2.16338 & 1.34812 & \textbf{1.34499} & 1.34593 \\
		0.3	& 3.27805 & \textbf{2.40153} & 3.05546 & 1.82199 & \textbf{1.43724} & 1.75610 & 1.22453 & 1.24810 & \textbf{1.21994} \\
		0.4	& 2.61641 & \textbf{1.63390} & 2.33662 & 1.54989 & \textbf{1.16887} & 1.46534 & 1.14507 & 1.19631 & \textbf{1.13979} \\
		0.5	& 2.08260 & \textbf{1.13827} & 1.77494 & 1.35101 & \textbf{1.04978} & 1.25567 & 1.09274 & 1.17069 & \textbf{1.08661} \\
		0.6	& 1.65897 & \textbf{1.02027} & 1.36093 & 1.20040 & \textbf{1.03720} & 1.11964 & 1.06255 & 1.15766 & \textbf{1.05701} \\
		0.7	& 1.32002 & \textbf{1.01350} & 1.11348 & 1.09659 & \textbf{1.03556} & 1.04569 & 1.04546 & 1.14416 & \textbf{1.04150} \\
		0.8	& 1.10725 & \textbf{1.01384} & 1.02188 & 1.03577 & 1.03439 & \textbf{1.01696} & 1.03711 & 1.12951 & \textbf{1.03565} \\
		0.9	& 1.02134 & 1.01315 & \textbf{1.00646} & 1.01364 & 1.03285 & \textbf{1.01029} & 1.03434 & 1.11631 & \textbf{1.03416} \\
		1.0 & \textbf{1.00480} & 1.01302 & \textbf{1.00480} & \textbf{1.00919} & 1.03261 & \textbf{1.00919} & \textbf{1.03393} & 1.10807 & \textbf{1.03393} \\	
		\hline
	\end{tabular}
	\label{table:n100}
\end{table}
